The \dealii Library, Version 9.4

### 2022-06-24 9.4/paper.tex
promote large-MPI to section

The major changes of this release are:
%
\begin{itemize}
  \item Advances in simplex- and mixed-mesh support (see Section~\ref{sec:simplex});
  \item Repartitioning of distributed meshes (see Section~\ref{sec:repartitioning});
  \item Advances in matrix-free infrastructure (see Section~\ref{sec:mf});
  \item Advances in multigrid infrastructure (see Section~\ref{sec:multigrid});
  \item CutFEM support (see Section~\ref{sec:cut});
  \item Experimental integration of the Computational Geometry Algorithms Library (CGAL) (see Section~\ref{sec:cgalwrappers});
  \item Performance improvements in the particle infrastructure (see Section~\ref{sec:particles});
  \item Improvements to unstructured communication (see Section~\ref{sec:CA});
  \item Three new tutorial programs and one new code gallery program (see Section~\ref{subsec:steps}).
\end{itemize}
%

While all of these major changes are discussed in detail in
Section~\ref{sec:major}, there
are a number of other noteworthy changes in the current \dealii release,
which we briefly outline in the remainder of this section:
%
\begin{itemize}
%  \item \texttt{AffineConstraints::make\_consistent\_in\_parallel()} allows
%  to make constraints consistent in parallel.
  \item The \texttt{DataOutResample} class interpolates values defined on one
  triangulation onto a second potentially unrelated triangulation.
  By using this class, one can output the result obtained on an
  unstructured mesh on a structured one (which might facilitate a more
  memory-efficient storage format, for example if this second
  triangulation is a uniformly refined rectangle or box), or one can create a slice in 3D.
  \item The new member function \texttt{find\_point\_owner\_rank()} of
        \texttt{parallel\allowbreak ::distributed::\allowbreak Tri\allowbreak angulation} allows one to find the MPI
  ranks of cells containing specified points.
  It is communication-free and leverages the functionality of \pfrst (>v.2.2).
  Its algorithm is described in \cite{burstedde2020parallel}. This information will
  enable efficient construction of the
  communication pattern used in the class \texttt{Utilties::\allowbreak MPI::\allowbreak RemotePointEvaluation}. Furthermore, this function could be used in the future to allow
  particle simulations in which particle movement is not
  limited by CFL conditions, as done in \cite{mirzadeh2016parallel}.
  \item The new function
  \texttt{GridGenerator::pipe\_junction()}
  generates a triangulation of three cone-shaped pipes that cross at a bifurcation point in any possible configuration.
  A manifold description is applied to the boundary, which can be extended into the volume via transfinite interpolation \cite{Gordon82} using the \texttt{TransfiniteInterpolationManifold} class \cite{dealII90}.
  \item A new DoF renumbering function \texttt{DoFRenumbering::support\_point\_wise()} which groups together
  shape functions by their support point. This functionality is useful in both developing nodal schemes since, e.g., the $x$, $y$, and $z$
  velocities at a point will be consecutive in the solution vector. It also improves interoperability with external libraries which expect
  data in this format.
  \item A new module \texttt{Utilities::MPI::LargeCount} which enables sending and receiving MPI messages containing more than $2^{31}$ objects.
  This library either uses the new MPI-4 functions, such as \texttt{MPI\_Send\_c()}, or an internal implementation of large objects for
  compatibility with MPI-3.
  \item The \texttt{FEInterfaceValues} class, which computes common quantities at the interface of two cells, has been overhauled to make it
  more consistent with the rest of the library and use more intuitive names for functions. For example,
  \texttt{FEInterfaceValues::jump\_gradient()} is now \texttt{FEInterfaceValues::jump\_in\_shape\_gradients()}. Several new
  functions, such as \texttt{FEInterfaceValues::get\_jump\_in\_function\_values()}, have also been added.
  \item Vectors attached to \texttt{DataOut} do not need to be in ghosted state anymore. Internally, we create a copy of the vector with appropriate ghosting.
\end{itemize}
%
The changelog lists more than 100 other features and bugfixes.

@@

>>>>

The major changes of this release are:
%
\begin{itemize}
  \item Advances in simplex- and mixed-mesh support (see Section~\ref{sec:simplex});
  \item Repartitioning of distributed meshes (see Section~\ref{sec:repartitioning});
  \item Advances in matrix-free infrastructure (see Section~\ref{sec:mf});
  \item Advances in multigrid infrastructure (see Section~\ref{sec:multigrid});
  \item CutFEM support (see Section~\ref{sec:cut});
  \item Experimental integration of the Computational Geometry Algorithms Library (CGAL) (see Section~\ref{sec:cgalwrappers});
  \item Performance improvements in the particle infrastructure (see Section~\ref{sec:particles});
  \item Support for large MPI buffers and parallel I/O (see Section~\ref{sec:large-mpi});
  \item Improvements to unstructured communication (see Section~\ref{sec:CA});
  \item Three new tutorial programs and one new code gallery program (see Section~\ref{subsec:steps}).
\end{itemize}
%

While all of these major changes are discussed in detail in
Section~\ref{sec:major}, there
are a number of other noteworthy changes in the current \dealii release,
which we briefly outline in the remainder of this section:
%
\begin{itemize}
%  \item \texttt{AffineConstraints::make\_consistent\_in\_parallel()} allows
%  to make constraints consistent in parallel.
  \item The \texttt{DataOutResample} class interpolates values defined on one
  triangulation onto a second potentially unrelated triangulation.
  By using this class, one can output the result obtained on an
  unstructured mesh on a structured one (which might facilitate a more
  memory-efficient storage format, for example if this second
  triangulation is a uniformly refined rectangle or box), or one can create a slice in 3D.
  \item The new member function \texttt{find\_point\_owner\_rank()} of
        \texttt{parallel\allowbreak ::distributed::\allowbreak Tri\allowbreak angulation} allows one to find the MPI
  ranks of cells containing specified points.
  It is communication-free and leverages the functionality of \pfrst (>v.2.2).
  Its algorithm is described in \cite{burstedde2020parallel}. This information will
  enable efficient construction of the
  communication pattern used in the class \texttt{Utilties::\allowbreak MPI::\allowbreak RemotePointEvaluation}. Furthermore, this function could be used in the future to allow
  particle simulations in which particle movement is not
  limited by CFL conditions, as done in \cite{mirzadeh2016parallel}.
  \item The new function
  \texttt{GridGenerator::pipe\_junction()}
  generates a triangulation of three cone-shaped pipes that cross at a bifurcation point in any possible configuration.
  A manifold description is applied to the boundary, which can be extended into the volume via transfinite interpolation \cite{Gordon82} using the \texttt{TransfiniteInterpolationManifold} class \cite{dealII90}.
  \item A new DoF renumbering function \texttt{DoFRenumbering::support\_point\_wise()} which groups together
  shape functions by their support point. This functionality is useful in both developing nodal schemes since, e.g., the $x$, $y$, and $z$
  velocities at a point will be consecutive in the solution vector. It also improves interoperability with external libraries which expect
  data in this format.
  \item The \texttt{FEInterfaceValues} class, which computes common quantities at the interface of two cells, has been overhauled to make it
  more consistent with the rest of the library and use more intuitive names for functions. For example,
  \texttt{FEInterfaceValues::jump\_gradient()} is now \texttt{FEInterfaceValues::jump\_in\_shape\_gradients()}. Several new
  functions, such as \texttt{FEInterfaceValues::get\_jump\_in\_function\_values()}, have also been added.
  \item Vectors attached to \texttt{DataOut} do not need to be in ghosted state anymore. Internally, we create a copy of the vector with appropriate ghosting.
\end{itemize}
%
The changelog lists more than 100 other features and bugfixes.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Support for large MPI buffers and parallel I/O}
\label{sec:large-mpi}

   A new module \texttt{Utilities::MPI::LargeCount} which enables sending and receiving MPI messages containing more than $2^{31}$ objects.
  This library either uses the new MPI-4 functions, such as \texttt{MPI\_Send\_c()}, or an internal implementation of large objects for
  compatibility with MPI-3.
